The Impact of Accretion Disk Winds on the Optical Spectra of Cataclysmic Variables

### 2015-04-16 draft_mnras_arxiv.tex
ready for arxiv hopefully

%%%% Various options for document class.
%\documentclass[usenatbib, a4paper]{preprint}
\documentclass[preprint, a4paper, 11pt]{aastex}
%%\documentclass[twocolum]{revtex4}
%%\documentclass{report}
%%\documentclass[useAMS,usenatbib, onecolumn]{mn2ejm}

@@

\author[Matthews et al.]{J.~H.~Matthews,$^1$ C.~Knigge,$^1$ K.~S.~Long,$^2$ S.~A.~Sim,$^3$ and N.~Higginbottom$^4$
\medskip  
\\$^1$School of Physics and Astronomy, University of Southampton, Highfield, Southampton, SO17 1BJ, UK
\\$^2$Space Telescope Science Institute, 3700 San Martin Drive, Baltimore, MD 21218, USA
\\$^3$School of Mathematics and Physics, Queens University Belfast, University Road, Belfast, BT7 1NN, Northern Ireland, UK
\\$^4$Department of Astronomy, University of Las Vegas, Las Vegas, NV 89119, USA}

%%\author{J. H. Matthews, C. Knigge, K. S. Long, S. A. Sim \& N. Higginbottom}

@@

\begin{figure}	%fullpage
\centering
\includegraphics[width=0.7\textwidth]{figures/fig1.eps}
\caption{
Optical spectra of three nova-like variables: 
RW Sex (top; Beuermann et al. 1992),
IX Vel (top middle; A. F. Pala \& B. T. Gaensicke, private communication) 
and RW Tri in and out of eclipse (bottom two panels; Groot et al. 2004).
The data for RW Sex and RW Tri were digitized from the respective publications,
and the IX Vel spectrum was obtained using the XSHOOTER spectrograph 
on the Very Large Telescope on 2014 October 10.
These systems have approximate inclinations of $30^\circ$, $60^\circ$ and $75^\circ$ 
(see section 5.4) respectively. 
The trend of increasing Balmer line emission with inclination can be seen.
In RW Tri strong single-peaked emission in the Balmer lines is seen even
in eclipse, indicating that the lines may be formed in a spatially
extensive disk wind, and there is even a suggestion 
of a (potentially wind-formed) recombination continuum in the eclipsed
spectrum. We have attempted to show each spectrum over a similar dynamic range.
}
\label{novalikes}
\end{figure}

@@

% \section{Sensitivity to Free Parameters}
% \label{sec:free_params}

% We have demonstrated that one can achieve a more
% realistic optical spectrum with small changes to the wind prescription; 
% specifically by altering just two kinematic parameters which increase the emission measure
% of the wind plasma. However, it may also be possible to achieve this by altering 
% other free parameters such as $\dot{M}_W$, the opening angles of the wind and the 
% inner and outer launch radii. Increasing the mass loss rate of the wind or volume of 
% the emitting area would

% We plan to explore the effect of these parameters

>>>>

\documentclass[useAMS,usenatbib]{mn2e_arxiv_submit}
%%%% Various options for document class.

@@

\author[Matthews et al.]{J.~H.~Matthews,$^1$\thanks{E-mail: jm8g08@soton.ac.uk} C.~Knigge,$^1$ K.~S.~Long,$^2$ S.~A.~Sim,$^3$ and N.~Higginbottom$^4$
\medskip  
\\$^1$School of Physics and Astronomy, University of Southampton, Highfield, Southampton, SO17 1BJ, UK
\\$^2$Space Telescope Science Institute, 3700 San Martin Drive, Baltimore, MD 21218, USA
\\$^3$School of Mathematics and Physics, Queens University Belfast, University Road, Belfast, BT7 1NN, Northern Ireland, UK
\\$^4$Department of Astronomy, University of Las Vegas, Las Vegas, NV 89119, USA}

\date{Accepted, 15 April 2015. Received, 8 April 2015; in original form, 26 January 2015.}
%%\author{J. H. Matthews, C. Knigge, K. S. Long, S. A. Sim \& N. Higginbottom}

@@

\begin{figure*}
\centering
\includegraphics[width=0.7\textwidth]{figures/fig1.eps}
\caption{
Optical spectra of three nova-like variables: 
RW Sex (top; Beuermann et al. 1992),
IX Vel (top middle; A. F. Pala \& B. T. Gaensicke, private communication) 
and RW Tri in and out of eclipse (bottom two panels; Groot et al. 2004).
The data for RW Sex and RW Tri were digitized from the respective publications,
and the IX Vel spectrum was obtained using the XSHOOTER spectrograph 
on the Very Large Telescope on 2014 October 10.
These systems have approximate inclinations of $30^\circ$, $60^\circ$ and $75^\circ$ 
(see section 5.4) respectively. 
The trend of increasing Balmer line emission with inclination can be seen.
In RW Tri strong single-peaked emission in the Balmer lines is seen even
in eclipse, indicating that the lines may be formed in a spatially
extensive disk wind, and there is even a suggestion 
of a (potentially wind-formed) recombination continuum in the eclipsed
spectrum. We have attempted to show each spectrum over a similar dynamic range.
}
\label{novalikes}
\end{figure*}

@@
